Incorporating Periodic Variability in Hidden Markov Models for Animal Movement

### 2016-08-03 bmc_template/manuscript.tex
I'll fill in additional files and sup
Minor touch ups on additional files later

GPS collars were fitted to 18 Florida panthers in 2005-2012 by Florida
Fish and Wildlife and Conservation Commission staff using
trained hounds and houndsmen. Of these animals, 13 had 
sufficient data to be used by van de Kerk et al.\cite{kerk2015hidden}.
Here we focus on the four cats with the most data (all with approximately 10,000-15,000
observations: see Table~1 in Supplementary Material), 
in part because our goal is to understand
the issues that arise when simple models are fitted to large data sets, and 
in part because the general trend in telemetry studies is toward larger data sets.  
As is typical in studies of animal movement, 
we took first differences of the data by decomposing
contiguous sequences of hourly GPS coordinates into 
successive step lengths (in meters) and turning angles (in radians)
\cite{turchin1998quantitative,kerk2015hidden}.

@@

@@

>>>>

GPS collars were fitted to 18 Florida panthers in 2005-2012 by Florida
Fish and Wildlife and Conservation Commission staff using
trained hounds and houndsmen. Of these animals, 13 had 
sufficient data to be used by van de Kerk et al.\cite{kerk2015hidden}.
Here we focus on the four cats with the most data (all with approximately 10,000-15,000
observations: see Table~1), 
in part because our goal is to understand
the issues that arise when simple models are fitted to large data sets, and 
in part because the general trend in telemetry studies is toward larger data sets.  
As is typical in studies of animal movement, 
we took first differences of the data by decomposing
contiguous sequences of hourly GPS coordinates into 
successive step lengths (in meters) and turning angles (in radians)
\cite{turchin1998quantitative,kerk2015hidden}.

@@

\section*{Funding}
 NSERC?

@@

\section*{Figures}
  \begin{figure}[h!]
  % \includegraphics[width=\maxwidth]{figure/acf_plot15-1}
  \caption{\csentence{Simulation Results} BIC-optimal state frequency for 2-6 state HMMs with and without covariate transition on 100 two-state hidden Markov models with covariate transitioning simulations.}
      \end{figure}

\begin{figure}[h!]
  \caption{\csentence{Sample figure title.}
      Figure legend text.}
      \end{figure}

\section*{Tables}
\begin{table}[h!]
\caption{Cat ID}
      \begin{tabular}{cccc}
        \hline
           & van de Kerk 2015  & IR@UF   & Number of Observations\\ \hline
         & 130 & 1 & 10286\\
         & 131 & 2  & 9458\\
         & 48 & 14  & 14645\\
         & 94  & 15   & 10250\\ \hline
      \end{tabular}
\end{table}
